\section{Overview}
\hspace{.5cm} Range and loiter time have been explored in the field of aeronautics by many individuals and companies, seeking to maximize both separately. However, since there is little utility for such use in a commercial environment, the trade-offs of range and loiter time for an aircraft have not been widely explored. The National Air and Space Intelligence Center (NASIC) seeks an optimization tool that identifies the range and loiter time trade-offs while minimizing error. Customers of NASIC are constructing aircraft mission plans and are looking for a spectrum of flight plans that meet their mission criteria. Analysts are currently using labor-intensive methods to provide range, radius, and time estimates for specific aircraft configurations. As a result, improved methods integrated into the process could result in significant time and cost savings. 

\section{Background}

\hspace{.5cm}The mission planning tool used by the National Air and Space Intelligence Center allows for a selection of aircraft, standardized load out, and flight profile. The outputs of the current tool are mission range or loiter time depending on initial user inputs and, depending on the feasibility of those inputs, may output an error. The program mainly operates from a fuel constrained perspective and provides the outputs based on fuel reserve after user-defined parameters such as warm up, take-off, cruise altitude, length of combat, and fuel reserve. \par
The high fidelity of the mission planning tool allows for specific points to be found and then a trade-off of loiter time and range is found by interpolating between these points which are at a close proximity. This aspect of finding the frontier of loiter time and range is time consuming and must be done by hand by analysts familiar with the mission planning tool. The intent to find a trade-off is similar to Snyder \cite{Tradeoffs} finding the performance tradeoffs in various rotocraft. Some have used the simplification of equations to maximize range \cite{breguetRangeEqn, OptimizeBreguet}, while Raymer \cite{LoiterTimeFromRange} found methods of approximating endurance from range at specific points. Extensions of this problem in Alighanbari et al \cite{Alighanbari} formulated an optimization problems with endurance constructed as an objective and timing as the constraints of multiple UAV control. 

\section{Motivation}
\hspace{.5cm}The current method of deriving an optimal range and loiter time for a customer with neither given as a parameter gives results that are accurate within five percent of actual, but are time consuming and inefficient. Additionally, the sensitivity of the current problem is unknown, given that the current method requires tabular calculations. The use of goal programming and optimization methods can be used to leverage the parameters in this dynamic problem and simplify the initial model. The geometric equivalence of the current solution method may be able to be used as a backbone for finding the vertical distance of two intersecting polynomials, representing aircraft's ingress to a range and egress to a base, using the result as an objective.\par
The primary objective of this research is to develop an efficient tool to accurately find the frontier of optimal ranges and loiter time for customers seeking options for their aircraft. A secondary objective is to find a full solution for all possible ranges and loiter times at multiple altitudes with as few runs as possible, illustrating the trade-offs between a longer range or a longer loiter time and applying these findings to a relevant assignment routing problem. \par
In Chapter 2, a review is conducted of current methodologies involving the estimation of range and flight time through various equations and their applications. In Chapter 3, a new methodology is presented to estimate the tradeoff frontier of range and loiter time for specific aircraft flight characteristics and applied to a geographic scenario. In Chapter 4, this method is tested against a known high fidelity model for accuracy. Chapter 5 will focus on the application of this methodology to an assignment problem. Finally, Chapter 6 will conclude with insights gained during the process and propose further research and methods to hone and apply the new methodology.

